\documentclass[a4paper,12pt]{amsbook}
\usepackage{physics}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{mathpazo}
\usepackage{microtype}
\providecommand{\tb}{\textbackslash}
\newcommand{\0}{{$|0\rangle$}}
\newcommand{\1}{{$|1\rangle$}}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{listings}
\usepackage{xcolor}
\pagecolor{black}
\color{white}
\usepackage{parskip}
\setlength{\parindent}{0pt}

\begin{document}

\section{inquiry}

\begin{enumerate}
\item Density matrices are a way to represent states. A density matrix is used to represent mixed states ie if you dont know the state of a system but you know that it is one among a bunch of states, you can weight the projectors of each state and sum them up to get their corresponding density matrix. This raises a few questions: \begin{enumerate} \item why projectors \item why sum the scaled projectors \item why scale them probabilities \end{enumerate} 
\item The density matrix of a pure state with probability 1 is just the projector of that state. The entries in the projectors of such states get us information about the probability of that basis state occuring; this interpretation works for the diagonal elements, but what about the off diagonal elements which are coefficients of outer product of orthogonal basis states?
\item Why sum the projectors? because it is a linear combination? why? because they are all the different possibilities? Then how is the linearity in the superposition of a pure state distinct from the linearity in the different pure states of a mixed state?
    \item Why is the first bell state so peculiar? Why is the whole system in a pure state but the subsystems in mixed states. Is the mixedness then a resource, an inalienable part of entanglement? Is it that we may choose where the mixedness will appear in the system, by making a trade off (with purity), but can never get rid of it? 
\end{enumerate}

\section{notes}
\begin{enumerate}
    \item What are density matrices? Alternative forumlation to represent quantum states.
    \item Properties of density matrices:\begin{enumerate} \item hermiticity \item positive semi definite \item trace 1 \item projector \end{enumerate}
\end{enumerate}

\end{document}
